The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-07-19 method.tex
add an assumption that one provider can push one order once
specify the suppose

\subsubsection{Assumptions and notation}

@@

\subsubsection{User agent} % (fold)
\label{ssub:user_agent}

% subsubsection user_agent (end)

\subsubsection{Platform agent} % (fold)
\label{ssub:platform_agent}

% subsubsection platform_agent (end)

>>>>

\subsubsection{Assumptions and notation}
\begin{itemize}
    \item one provider can publish only one order at one time;
    \item service quality give the initial rank, the product quality depends on the service quality, review depends on the service quality, and the rank depends on the review;
    \item when it comes to rank value, we refer two different rank values: user rank(provider) and service rank, their relationship should be determined.
\end{itemize}

@@

\subsubsection{Demander agent} % (fold)
\label{ssub:demander_agent}
After pricing, chose the provider and the amount considering the time limit of the project and the budget.
% subsubsection demander_agent (end)

\subsubsection{Provider agent} % (fold)
\label{ssub:provider_agent}
Pricing function specify two main parts:
unit cost and
provided amount
% subsubsection provider_agent (end)

\subsubsection{Complex user agent} % (fold)
\label{ssub:complex_user_agent}

% subsubsection complex_user_agent (end)

\subsubsection{Platform agent} % (fold)
\label{ssub:platform_agent}
matching the 
% subsubsection platform_agent (end)
